Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-11-22 Docs/IJES/journal.tex
including initial version of IJES

\documentclass[prodmode,acmtodaes]{acmsmall} % Aptara syntax

\usepackage{listings} % Codes
%\lstset{
 % language=C,                % choose the language of the code
 % numbers=left,                   % where to put the line-numbers
 % stepnumber=1,                   % the step between two line-numbers.        
 % numbersep=5pt,                  % how far the line-numbers are from the code
 % backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
 % showspaces=false,               % show spaces adding particular underscores
 % showstringspaces=false,         % underline spaces within strings
 % showtabs=false,                 % show tabs within strings adding particular underscores
 % tabsize=2,                      % sets default tabsize to 2 spaces
 % captionpos=b,                   % sets the caption-position to bottom
 % breaklines=true,                % sets automatic line breaking
 % breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
 % title=\lstname,                 % show the filename of files included with \lstinputlisting;
%}

\usepackage{mathtools} % Serve para as equacoes

%Montar os Gráficos, cores e divisões.
\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}  
\usepackage{tabularx} % in the preamble
\usepackage{graphicx} %Imagens
\renewcommand{\lstlistingname}{Algorithm}
%\usepackage{minted}
%\usemintedstyle{bw}

\newcolumntype{C}[1]{>{\Centering}m{#1}}
\renewcommand\tabularxcolumn[1]{C{#1}}
\usepackage{tabularx,ragged2e,booktabs,caption}

%\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial

\usepackage{hyphenat}
\hyphenation{ESBMC par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

%\usepackage[skip=\baselineskip]{caption}
%\captionsetup[lstlisting]{font={small,tt}}

% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2015}
\acmMonth{3}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{0000001.0000001}

%ISSN
\issn{1234-56789}

% Document starts
\begin{document}

% Page heads
\markboth{A. Trindade et al.}{Multi-Core Model Checking and Maximum Satisfiability Applied to HW/SW Partitioning}

@@

% Title portion
\author{
Alessandro Trindade
\affil{Federal University of Amazonas}
Hussama Ismail
\affil{Federal University of Amazonas}
Edilson Galv\~ao\
\affil{Federal University of Amazonas}
Renato Degelo\
\affil{Federal University of Amazonas}
Helder Silva
\affil{Federal University of Amazonas}
Lucas Cordeiro\affil{Federal University of Amazonas}
}

% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010583.10010682.10010684.10010686</concept_id>
<concept_desc>Hardware~Hardware-software codesign</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010583.10010682.10010712.10010715</concept_id>
<concept_desc>Hardware~Software tools for EDA</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010992.10010998.10003791</concept_id>
<concept_desc>Software and its engineering~Model checking</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010992.10010998.10010999</concept_id>
<concept_desc>Software and its engineering~Software verification</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Hardware~ Hardware-software codesign}
\ccsdesc[500]{Hardware~ Software tools for EDA}
\ccsdesc[500]{Software and its engineering~ Model checking}
\ccsdesc[500]{Software and its engineering~ Software verification}

%
% End generated code
%

%\terms{Design, Algorithms, Performance}

\keywords{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP.}

%\acmformat{Gang Zhou, Yafeng Wu, Ting Yan, Tian He, Chengdu Huang, John A. Stankovic,
%and Tarek F. Abdelzaher, 2010. A multifrequency MAC specially
%designed for  wireless sensor network applications.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

\begin{bottomstuff}
A. Trindade, H. Ismail, R. Degelo, and E. Galv\~ao \\
Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com \\ 
\\
H. Silva, and L. Cordeiro \\
Federal University of Amazonas, Brazil\\
prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br      \\
\end{bottomstuff}

@@

%---------------------------------
\section{Introduction}
\label{Introduction}
%---------------------------------

@@

%In any HW and SW design of complex systems, more time is spent on verification than on construction~\cite{Baier2008}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Software (and systems) may be viewed as mathematical objects with behavior that is, in principle, well determined. This makes it possible to specify software using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the software meets its specification ~\cite{Clarke2009}. Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors. Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner. The system models are accompanied by algorithms that systematically explore all the states of the system model.

@@

%Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}. In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}. However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.

@@

% in which its main function is to check the satisfiability of logical formulas based on objective functions

\textbf{Contributions.} The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems. Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool, which is typically used for software verification, in order to formulate and solve optimization problems within the logical context of constraints. Experimental results show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach. Although there is no single tool for efficiently solving all HW-SW partitioning problems, we show that the MaxSMT solver $\nu$Z is faster than other state-of-the-art optimization tools for small- and medium-size optimization problems.  To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.

\textbf{Availability of Data and Tools. }Our experiments are based on a set of publicly available benchmarks. All benchmarks, tools, and results of our evaluation are available on a supplementary web page\footnote{http://esbmc.org/}.

@@

%----------------------------------------------
\section{Background}
\label{background}
%----------------------------------------------

@@

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}. 
%In the design, construction, and maintenance of any engineering system, engineers have to make many technological and managerial decisions at several stages. The ultimate goal of all such decisions is either to minimize the effort required or to maximize the desired benefit. Because the effort required or the benefit desired in any practical situation can be expressed as a function of certain decision variables, optimization can be defined as the process of finding the conditions that give the maximum or minimum value of a function~\cite{Rao2009}.
There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints

@@

Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}. In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style. GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations ({\it i.e.},\:$C \land \neg P$), which are checked for satisfiability by an SMT solver.

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1]{figures/esbmc-arch-new.pdf} 
	\caption{ESBMC architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{matlab}
%int k;
%#pragma omp parallel for
%for (k = 0; k < 10; k++)
%  a[k] = 2*k;
%\end{minted}
%\caption{OpenMP basic Example.}
%\label{lst:example}
%\end{listing}

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\small,language=C,caption={OpenMP basic Example.},label={lst:example},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

@@

%SMT decides the satisfiability of first-order formulas using a combination of different background theories and thus generalizes propositional satisfiability by supporting uninterpreted functions, linear and nonlinear arithmetic, bitvectors, tuples, arrays, and other decidable first-order theories.

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%              framesep=2mm]{c++}
%(Declare-Const K Int) 
%(Declare-Const W Int)
%(assert (< K 2)) 
%(assert (< (- W K) 1))
%(maximize (+ K W)) 
%(check-sat)
%\end{minted}
%\caption{Example of SMT formula using $\nu$Z.}
%\label{vZ}
%\end{listing}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.3]{figures/vzArch.png} 
	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
%
\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}

\vspace{2 mm}
\noindent
and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
%
%
%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j).
\end{align}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
% Initialize Variables 
% Declare number of nodes and edges
% Declare hardware cost of each node as array (h)
% Declare software cost of each node as array (s)
% Declare communication cost of each edge (c)
% Declare the initial software cost of (S0)
% Declare transposed incidence matrix graph G (E)
% Define the solutions variable (Xi) as Boolean
% main {
%  For TipH = 0 to Hmax Do {
%   populate Xi with nondeterministic/test values
%   Calculate s(1-x)+c|Ex| and store at variable
%   Requirement isued by Assume (Variable <= S0)
%   Calculate Hp cost Based on value tested of Xi
%   Violation check with Assert(Hp > TipH)
%  }
% }
%\end{minted}
%\caption{Pseudocode describing sequential ESBMC}
%\label{Pseudocode-describing-ESBMC}
%\end{listing}

@@

%In the multi-core ESBMC algorithm, the only difference is the fact that the value of $ TipH $ and its range is not declared in the algorithm, %as shown in ESBMC Pseudocode. The proposed approach is invoked for each test problem, as follows:
%$ esbmc-parallel <Filename.c> \; <hminvalue> \; <Hmax> $

%Where $ <Filename.c> $ is the optimization problem described in ANSI-C format, $  <hminvalue> $ is the minimum (zero to HW-SW partitioning %problem) and $ <Hmax> $ is the maximum hardware cost for the specified problem.

%Therefore, the algorithm starts different ESBMC instances using different optimization values, in ascending order, for $ Hmax $ in order to %find a violation. If all instances finish and no violation is found, then multi-core ESBMC starts new $ N $ instances. When a violation is %found, it reports time and hardware cost. If multi-core ESBMC tests all the possibilities for the hardware cost and has not found a violation, %then it reports: $ Violation not found $.

@@

To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.
\begin{figure}[h]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ss.pdf} 
	\caption{ESBMC-SS approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[h]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ps.pdf} 
	\caption{ESBMC-PS approach.}
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-pb.pdf} 
	\caption{ESBMC-PB approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1.0, height=75px]{figures/Fig4.png}
	\caption{Binary step calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
%  GetNextStep(){
%  int largestChunk = -1;
%  chunk largest;
%  for each(chunk in chunks){
%     if(chunk.right - chunk.left > largestChunk){
%           largestChunk = chunk.right - chunk.left;
%           largest = chunk;
%     }
%   }	
%   chunks.remove(largest);	
%   int median = largest.left + floor((largest.right - largest.left) / 2)
%   if(median > 0){
%      if(largest.right - largest.left > 1)
%         chunks.add(new chunk(largest.left, median - 1));	
%      if(largest.right != largest.left)
%         chunks.add(new chunk(median + 1, largest.right);
%    }
%   return median;
% }
%\end{minted}
%\caption{Steps calculation using intervals.}
%\label{Steps-Calculation-using-Intervals}
%\end{listing}
\vspace {2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
    if(chunk.right - chunk.left > largestChunk){
      largestChunk = chunk.right - chunk.left;
      largest = chunk;
    }
  }	
  chunks.remove(largest);	
  int median = largest.left + floor((largest.right - largest.left) / 2);
  if(median > 0){
    if(largest.right - largest.left > 1)
      chunks.add(new chunk(largest.left, median - 1));	
    if(largest.right != largest.left)
      chunks.add(new chunk(median + 1, largest.right);
  }
  return median;
}
\end{lstlisting}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
% step = controller.GetNextStep();
% int pid = ExecuteStep(step);
% while(isRunning(pid)){
%   if(!controller.isNeeded(step))
%    kill(pid);
% }
%\end{minted}
%\caption{Worker sample.}
%\label{worker-sample}
%\end{listing}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
%--Initialize Variables
%  Create vZ context 
%  Create binary vector (x)
%  Declare number of nodes, edges and S0
%  Declare hardware cost of each node as array (h) 
%  Declare software cost of each node as array (s)
%  Declare communication cost of each edge (c)
%  Declare transposed incidence matrix graph G (E)
%--Arithmetic Expressions
%  SC = s(1-x)
%  CMC = c*|EX|
%  Fobj =  x[i] * h[i]
%--Assert Constraints
%  Add constraints (SF + CMC <= S0)
%  Add constraints to minimize Fobj
%  Check Model
%  Print Result
%\end{minted}
%\caption{Pseudocode describing ESBMC-$\nu$Z.}
%\label{vZ-pseudocode}
%\end{listing}

@@

%----------------------------------------------
\subsection{Description of Benchmarks}
\label{Benchmarks-Description}
%----------------------------------------------

\vspace{1.5 mm}
\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=4pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{8.9cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree \cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}. The nodes in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area. The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}. The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks. From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).

%\begin{table}[h]
%\centering
%\caption {Description of Benchmarks.}
%\small
%\sffamily\small
%\tabulinesep=6pt

%\label{Description-of-Benchmarks}
%\end{table}

%----------------------------------------------
\subsection{Experimental Results}
\label{Experimental-Results}
%----------------------------------------------
%
\begin{table*}[h]
  \centering
  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
\\
 &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
\cmidrule(r){3-9}

&\textbf{\normalsize{Nodes}} &\normalsize{25} & \normalsize{21} & \normalsize{26} & \normalsize{150} & \normalsize{329} & \normalsize{261} & \normalsize{417}\\
&\textbf{\normalsize{Edges}} &\normalsize{32} & \normalsize{48} & \normalsize{69} & \normalsize{331} & \normalsize{448} & \normalsize{442} & \normalsize{600}\\
&\textbf{\normalsize{S0}} &\normalsize{20} & \normalsize{10} & \normalsize{20} & \normalsize{50} & \normalsize{600} & \normalsize{4578} & \normalsize{300} \\

%EXACT Solution
\bottomrule[1.5pt]
\rowcolors{1}{}{lightgray}

\multirow{4}{*}{\textbf{\normalsize{Exact Solution}}}
& & & & & & & & & \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
& & & & & & & & & \\

>>>>

%%%%%%%%%%%%%%%%%%%%%%
\documentclass{doublecol-new}
%%%%%%%%%%%%%%%%%%%%%%

\usepackage{natbib,stfloats}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{listings}
\renewcommand{\lstlistingname}{Algorithm}

\def\newblock{\hskip .11em plus .33em minus .07em}

\theoremstyle{TH}{
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corrolary}[lemma]{Corrolary}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{stheorem}[lemma]{Wrong Theorem}
\newtheorem{algorithm}{Algorithm}
}

\theoremstyle{THrm}{
\newtheorem{definition}{Definition}[section]
\newtheorem{question}{Question}[section]
\newtheorem{remark}{Remark}
\newtheorem{scheme}{Scheme}
}

\theoremstyle{THhit}{
\newtheorem{case}{Case}[section]
}

\makeatletter
\def\theequation{\arabic{equation}}

%\JOURNALNAME{\TEN{\it Int. J. System Control and Information
%Processing,
%Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}}%
%
%\def\BottomCatch{%
%\vskip -10pt
%\thispagestyle{empty}%
%\begin{table}[b]%
%\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
%\\[-12pt]
%Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
%\end{tabular*}%
%\vskip -30pt%
%%%\vskip -35pt%
%\end{table}%
%}
\makeatother

%%%%%%%%%%%%%%%%%
\begin{document}%
%%%%%%%%%%%%%%%%%

\setcounter{page}{1}

\LRH{A. Trindade et~al.}

\RRH{Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning}

\VOL{x}

\ISSUE{x}

\PUBYEAR{xxxx}

\BottomCatch

%\CLline

\PUBYEAR{2012}

\subtitle{}

@@

\authorA{Alessandro Trindade, Hussama Ismail}
\affA{Federal University of Amazonas \\
E-mail: \{alessandro.b.trindade, hussamaismail\}@gmail.com}

\authorB{Edilson Galv\~ao, Renato Degelo}
\affB{Federal University of Amazonas \\
E-mail: \{rdegelo, esj.galvao\}@gmail.com}

\authorC{Helder Silva, and Lucas Cordeiro}
\affC{Federal University of Amazonas \\
E-mail: prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br}

@@

\KEYWORD{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP.}

\REF{to this paper should be made as follows: Rodr\'{\i}guez
Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
corporate environmental disclosures on the internet: the case of
IBEX 35 Spanish companies', {\it International Journal of Metadata,
Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}

\begin{bio}
\textcolor{red}{
Manuel Pedro Rodr\'iguez Bol\'ivar received his PhD in Accounting at
the University of Granada. He is a Lecturer at the Department of
Accounting and Finance, University of Granada. His research
interests include issues related to conceptual frameworks of
accounting, diffusion of financial information on Internet, Balanced
Scorecard applications and environmental accounting. He is author of
a great deal of research studies published at national and
international journals, conference proceedings as well as book
chapters, one of which has been edited by Kluwer Academic
Publishers.\vs{9}}

\textcolor{red}{\noindent Bel\'en Sen\'es Garc\'ia received her PhD in Accounting at
the University of Granada. She is a Lecturer at the Department of
Accounting and Finance, University of Granada. Her research
interests are related to cultural, institutional and historic
accounting and in environmental accounting. She has published
research papers at national and international journals, conference
proceedings as well as chapters of books.\vs{8}}

\textcolor{red}{\noindent Both authors have published a book about environmental
accounting edited by the Institute of Accounting and Auditing,
Ministry of Economic Affairs, in Spain in October 2003.}
\end{bio}

@@

\section{Introduction}

@@

@@

@@

\subsection{Contributions}

The main contribution of the present study is to describe and evaluate a comprehensive SMT-based BMC approach in a multi-core architecture applied to solve HW-SW optimization problems. Additionally, we integrate the MaxSMT solver $\nu$Z into an off-the-shelf BMC tool, which is typically used for software verification, in order to formulate and solve optimization problems within the logical context of constraints. Experimental results show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach. Although there is no single tool for efficiently solving all HW-SW partitioning problems, we show that the MaxSMT solver $\nu$Z is faster than other state-of-the-art optimization tools for small- and medium-size optimization problems.  To the best of our knowledge, this is the first work to use a multi-core SMT-based verification and a MaxSMT solver to check for HW-SW partitioning problems in embedded systems.

\subsection{Availability of Data and Tools}

Our experiments are based on a set of publicly available benchmarks. All benchmarks, tools, and results of our evaluation are available on a supplementary web page\footnote{http://esbmc.org/}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\label{background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances~\cite{Rao2009}. There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints

@@

Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}. In particular, ESBMC compiles C/C$++$ code into equivalent GOTO-programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style. GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations ({\it i.e.},\:$C \land \neg P$), which are checked for satisfiability by an SMT solver.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
	\caption{ESBMC architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

\vspace{2 mm}
\begin{lstlisting}[label={lst:example}, language=C,numbers=left, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=b, caption={OpenMP basic Example.}]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

@@

@@

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.21]{figures/vzArch.png} 
	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}

\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}

\vspace{2 mm}
\noindent
and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}

\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j).
\end{align}

@@

@@

@@

To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.

\begin{figure}[h]
	\centering
  \includegraphics[scale=0.77]{figures/esbmc-ss.pdf} 
	\caption{ESBMC-SS approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[h]
	\centering
  \includegraphics[scale=0.77]{figures/esbmc-ps.pdf} 
	\caption{ESBMC-PS approach.}
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.77]{figures/esbmc-pb.pdf} 
	\caption{ESBMC-PB approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

@@

\begin{figure}[h!]
	\centering
  \includegraphics[scale=0.17]{figures/Fig4.png}
	\caption{Binary step calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
    if(chunk.right - chunk.left > largestChunk){
      largestChunk = chunk.right - chunk.left;
      largest = chunk;
    }
  }	
  chunks.remove(largest);	
  int median = largest.left + floor((largest.right - largest.left) / 2);
  if(median > 0){
    if(largest.right - largest.left > 1)
      chunks.add(new chunk(largest.left, median - 1));	
    if(largest.right != largest.left)
      chunks.add(new chunk(median + 1, largest.right);
  }
  return median;
}
\end{lstlisting}

@@

@@

@@
